---
title: "Brain and Body weight for animals"
author: "Austin Pray and Joe Bao"
date: "2/19/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- Data gathered from P. J. Rousseeuw and A. M. Leroy (1987) Robust Regression and Outlier Detection. Wiley, p. 57.
- The dataset comes from average brain and body weights for 28 species of land animals.
- body: body weight in kg.
- brain: brain weight in g.

```{r}
library(readr)
babw <- read_csv("data/Animals.csv")
ratiobabw <- transform(babw, new = brain / (body*1000))
rownames(ratiobabw) <- ratiobabw[,c(1)]
smallbabw = babw[,c(2,3)]
attach(smallbabw)
```

## Summary

```{r}
summary(smallbabw)
```

## Head

```{r}
head(smallbabw)
```

## Tail

```{r}
tail(smallbabw)
```

## Correlation

```{r}
cor(smallbabw)
```

## Brain and Body weight scatterplot

```{r}
plot(body~brain, main = "Brain and body weight", xlab = "body weight in KG", ylab = "brain weight in g", data = smallbabw)
```

## Brain and Body ratio dot plot

```{r}
dotchart(ratiobabw$new,labels=row.names(ratiobabw),cex=.7,
  	main="Ratio of brain to body weight", 
   xlab="Brain to body weight ratio")
```

## What we seek to learn

- We should be able to combine this data with other data on animal reproduction and determine if brain/body weight ratio has anything to do with animal reproduction and the average number of offpsring an animal will have in a lifetime.