---
title: "Coursebook"
author: "Austin Pray and Joe Bao"
date: "February 19, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## UT Dallas Coursebook

This was obtained from the https://coursebook.utdallas.edu/ 

We hope to classify professors by the prefixes of the courses they teach. We want to see if a professor that teaches in CS often cross-teaches in the Math department.

```{r}
library(readr)

coursebook = read.csv("data/utd-coursebook.csv")

summary(coursebook)
```

### Peek at the data

```{r}
head(coursebook)
tail(coursebook)
```

### Let's see the professors with highest number of classes

```{r}
topProfs = sort(table(coursebook$instructors), decreasing = T)
dotchart(head(topProfs, 20))
```

### Let's see the enrollment for departments

```{r}
aggregate(coursebook$enrollment, by=list(coursebook$dept), FUN=sum)
```

### Chord

```{r}
plot(coursebook$class.title, coursebook$enrollment)
```

## Analysis

I will use the following clustering algorithms:

- Hierarchical Clustering
- KNN Clustering
- K-Means Clusters


### KNN Clustering

```{r}
require(caTools)
require(kknn)
set.seed(101) 
sample = sample.split(coursebook, SplitRatio = .75)
train = subset(coursebook, sample == TRUE)
test  = subset(coursebook, sample == FALSE)
mod15 = kknn(coursebook$instructors ~ coursebook$enrollment + coursebook$asst.count, train, test, prob=TRUE)
prob <- attr(mod15, "prob")
prob <- ifelse(mod15=="1", prob, 1-prob)
px1 <- 
px2 <- mixture.example$px2
prob15 <- matrix(prob, length(px1), length(px2))
par(mar=rep(2,4))
contour(px1, px2, prob15, levels=0.5, labels="", xlab="", ylab="", main=
        "15-nearest neighbour", axes=FALSE)
points(x, col=ifelse(g==1, "coral", "cornflowerblue"))
gd <- expand.grid(x=px1, y=px2)
points(gd, pch=".", cex=1.2, col=ifelse(prob15>0.5, "coral", "cornflowerblue"))
box()
```

### K-means
